---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# saeHB.hnb

<!-- badges: start -->
<!-- badges: end -->

This package provides a function and datasets for area level of Small Area Estimation under Hurdle Negative Binomial Model using Hierarchical Bayesian (HB) Method.

## Author
Raka Ikmana, Azka Ubaidillah

## Maintaner
Raka Ikmana <221810548@stis.ac.id>

## Function

* `HurdleNB()` This function gives small area estimator under Hurdle Negative Binomial Model and is implemented to variable of interest (y) that assumed to be a HNB Distribution. The value of variable of interest must be a non-negative data count.

## Installation

You can install the development version of `saeHB.hnb` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rakaikmana/saeHB.hnb")
```

## Example

This is a basic example of using `HurdlenNB()` function to make an estimate based on synthetic data in this package

```{r example}
library(saeHB.hnb)
## For data without any non-sampled area
data(dataHNB)       # Load dataset

## For data with non-sampled area use dataHNBNs
## Fitting model
result <- HurdleNB(y ~ x1 + x2, data=dataHNB)
```

Small Area mean Estimates

```r
result$Est
```

Estimated model coefficient

```r
result$coefficient
```

Estimated random effect variances

```{r}
result$refVar
```


## References
* Hilbe, J. M. (2011). Negative Binomial Regression 2nd Edition. New York : Cambridge University Press. <doi:10.1017/CBO9780511973420>.
* Ntzoufras, I. (2009). Bayesian Modelling Using WinBUGS. New Jersey :  John Wiley & Sons, Inc.
* Rao, J.N.K & Molina. (2015). Small Area Estimation 2nd Edition. New Jersey : John Wiley & Sons, Inc. <doi:10.1002/9781118735855>.
